Dynamical dark energy constraints via clustering shells of SDSS-III BOSS galaxies

### 2017-06-22 Draft/Draft0.3.tex
minor changes

  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
  \affiliation{NAOC}
  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}

\begin{abstract}
We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effect, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

@@

%\section{Introduction}
{\it Introduction.}---
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
It is, therefore, crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation from redshift space to comoving space produces residual geometric distortions. 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

The main caveat of AP test is that,
because the radial distances of galaxies are inferred from observed redshifts,
AP tests are inevitably limited by peculiar motions of galaxies,
which leads to apparent anisotropy even if the adopted cosmology is correct.
The effect, known as redshift-space distortions (RSD),
is very difficult to be accurately modeled in the 2-point statistics of galaxy clustering \citep{Ballinger1996}.

As alternative methods, \cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs;
%Unfortunately this method is also seriously limited by RSD.
however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
this method is also seriously limited by RSD \citep{Jennings2011}.
\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
This approach has the advantage that the void regions are easier to model compared with dense regions,
but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve good statistics \citep{Qingqing2016}.

@@

In an effort to mitigate the RSD effect, \cite{Li2014} proposed utilizing the {\it redshift dependence} of the AP effect. 
The anisotropies produced by the RSD effect are, although large, close to uniform in magnitude over a wide range in redshift. 
However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence. 
In a later work, \cite{Li2015} developed the AP methodology 
which investigates the redshift dependence of galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   The distance dependence of shape distortion in four wrongly assumed cosmologies,
   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
   There are four perfect squares with their true shapes plotted in blue dashed lines.
   They are measured by an observer located at the origin, and the distances are computed in the two wrong cosmologies.
   The apparently distorted shapes are plotted in red solid lines.
   }
\end{figure*}

@@

\citep{Li2016} applied the AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
Combining the method with measurements of Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
baryon acoustic oscialltions (BAO), and $H_0$,
they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
By reducing the RSD effect, 
they are able to use the galaxy clustering down to 6 $h^{-1}$Mpc,
which is a major advance in extracting the cosmological information 
on small scales where galaxy clustering is strong and there are a lot of independent structures.

In this work as a continuation of the serious work we move forward to infer the constraints on dynamical dark energy.
We will present a slightly improved methodology to that of \citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen non-parametric approach could also be considered. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
$w(z) = w_0 + w_a \frac{z}{1+z}$. 
As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects varies with distance
in case of wrongly adopted $w_0$ or $w_a$.

@@

The spectroscopic sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed
\footnote{These correlations were computed using the public, kd-tree + MPI code called KSTAT \citep{kstat}.} 
as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalise these {\em clustering shells} as 
$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.

The right panel of Fig.\ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
But the shape of the tilted lines remain similar at different redshifts, which enables us avoiding RSD by looking at the redshift dependence.
The ``correct'' cosmological model is selected by minimising the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respective to the lowest redshift bin,
with systematic effects subtracted:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

@@

The number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the realtion of 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ in an ultra high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
The ``edge effects'' in case of one small pixel belonging to more than one large pixel
are treated by computing the fraction of the area.
We found that using the approximated method the computed 
$\hat\xi_{\Delta s}(\mu)$ in non-fiducial cosmologies suffer from
an error of $\approx0.5\%$, which is 10 times smaller than 
the statistical noise in the 2pCF.

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four ``chains'' in the CPL model, 
using a combination of four techniques:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
\footnote{http://pla.esac.esa.int/pla/\#cosmology}.
These chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed at $\sim$37 thounsands sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of AP method at these parameters, 
multiplying the sample likelihoods with ours and also correspondingly changing the sample weights,
and derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29,    
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift significantly,
the erro bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}, 
Adding our new AP constraints significantly reduces the allowable parameter space. 
We can also visualise this as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the AP method reduces the statistical errors by $\sim$30-40\%,
reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
This reveals the power of the our method in constraining the redshift evolution of dark energy.

@@

Finally, we performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that,
the result does not change if 
we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) near-LOS regions in the analysis,
decrease the number of bins to $n_{\mu}=15-20$,
change the range of clustering to $8-30 \rm Mpc/h$,
change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
exclude 1 or 2 high redshift bins,
or reduce the number of mocks to 1000.
%Constraints get weaker if increase $s_{\rm min}$,
%but are consistent with the original one.
%Even if we choose an extremely unrealistic fiducial cosmology, i.e. 
% $\Omega_m=0.11,\ w=-2.0$, the change in contour is still mild.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} on the systematic correction could influence on our final results.

@@

In \cite{Li2016} we proposed to constrain cosmological parameters via 
the redshift dependence of galaxy anisotropic clustering. 
This enables a robust Alcock-Paczynski test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy. 
Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

The AP method presented in this work has many advantages over the 'traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

@@

\begin{acknowledgments}
We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System). 
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, van putten Maurice, Graziano Rossi and Yi Wang for helpful discussions.
\end{acknowledgments}

>>>>

  \affiliation{School of Physics, Korea Institute for Advanced Study, 85 Heogi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
  \affiliation{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 305-348, Korea}
  \affiliation{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
  \affiliation{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}

\begin{abstract}
We use the anisotropic {\it clustering shells} of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016}, 
we present a novel use of the Alcock-Paczynski (AP) test via the small scales clustering difference between redshift bins. 
This differential measure appears to be a robust statistical tool which mitigates many systematic effects, 
allowing for competitive and unbiased constrains. 
A combination of CMB+BAO+SNIa+$H_0$+AP yields
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL).
Adding the AP method reduces the $w_0-w_a$ contour area by 50\%.
The method can be combined with the standard BAO method, 
increasing the science output of ongoing and future galaxy surveys by a factor of 2.
\end{abstract}

@@

%\section{Introduction}
{\it Introduction.}---
The  origin  of  the  accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Proposed mechanisms include  evolving  scalar  fields  remnant  from  the  big  bang, 
modifications to gravity,  and a  non-zero  vacuum energy \cite[see][for a comprehensive review]{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing dark energy models.

In recent years the Alcock-Paczynski (AP) test \citep{AP1979} applied to galaxy redshift samples \citep{Outram2004,Blake2011,Alam2016}, 
has allowed tight constraints to be placed on the background averaged distance scales, $D_A(z)$ and $H^{-1}(z)$.  
Assuming an incorrect cosmological model for the coordinate transformation between redshift space and comoving space, produces residual geometric distortions in the resultant galaxy distribution. 
These distortions are induced by the fact that measured distances along 
and perpendicular to the line of sight are fundamentally different. 
Measuring the ratio of galaxy clustering in the radial and transverse directions provides a probe of this AP effect.

@@

The main caveat of the AP test is due to the fact that 
the radial distances of galaxies are inferred from observed redshifts.
Thus AP tests are inevitably affected by peculiar motions of galaxies,
which leads to apparent anisotropy in the clustering signal, even if the adopted cosmology is correct.
The effect, known as redshift-space distortions (RSD),
is notoriously difficult to model accurately in the 2-point statistics of galaxy clustering \citep{Ballinger1996}.

As alternative methods, \cite{Marinoni2010} proposed using the symmetry properties of galaxy pairs;
however, since the peculiar velocity distorts the redshifts and changes the apparent tilt angles of galaxy pairs,
this method is also seriously limited by RSD \citep{Jennings2011}.
\cite{Ryden1995} and \cite{LavausWandelt1995} proposed another method using the apparent stretching of voids.
This approach has the advantage that the void regions are easier to model compared with dense regions,
but has limitations in that it utilizes only low density regions of the LSS and requires large samples to achieve competitive constraints \citep{Qingqing2016}.

@@

In an effort to mitigate the RSD effect, \cite{Li2014} proposed utilizing the {\it redshift dependence} of the AP effect. 
The clustering anisotropies produced by are, although large, close to uniform in magnitude over a wide range in redshift. 
However, if cosmological parameters are incorrectly chosen resulting in an AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence. 
In a later work, \cite{Li2015} developed an AP methodology 
that utilises the redshift dependence of the galaxy 2-point correlation function (2pCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).
As an illustration, Fig.\ref{fig_xy} shows how the shape distortion of objects (anisotropy of clustering signal) varies with distance (or redshift) when incorrect values of  $w_0$ or $w_a$ are used to infer distances.

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
   assuming a true cosmology of $\Omega_m=0.31$, $w=-1$.
   There are four perfect squares with their true shapes plotted in blue dashed lines.
   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
   The apparently distorted shapes are plotted in red solid lines.
   }
\end{figure*}

@@

\citep{Li2016} applied their AP method to galaxies from the 3rd incarnation of the Sloan Digital Sky Survey (SDSS-III).
Combining their method with measurements of the Cosmic Microwave Background (CMB), type Ia supernovae (SNIa), 
baryon acoustic oscillations (BAO), and $H_0$,
they obtained very tight constraints of $ \Omega_m = 0.301 \pm 0.006,\ w=-1.054 \pm 0.025$.
In reducing the RSD effect, 
they were able to use galaxy clustering on scales down to 6 $h^{-1}$Mpc,
which is a major advance in extracting cosmological information 
on small scales where galaxy clustering is strong and there are many independent structures.

In this paper, we continue to develop our previous methodology and proceed to infer the constraints on dynamical dark energy. We will present a slightly improved methodology to that of \citep{Li2016}, 
allowing for faster likelihood estimation and thus the exploration of larger, higher dimensional parameter spaces. 
The methodology we will present here, can be applied to any model of dynamical dark energy, 
or indeed any appropriately chosen parametric or non-parametric decomposition of the cosmic expansion history. 
However, as a first step, in this paper we will focus on the widely used Chevallier-Polarski-Linder (CPL) parametrization
$w(z) = w_0 + w_a \frac{z}{1+z}$.

@@

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \cite{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The number density of galaxies and the redshift binning scheme is plotted in the left panel of Fig.\ref{fig_TpCF}.

Following our previous methodology \citep{Li2016}, the information of small-scale anisotropic clustering is computed
\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
as $\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds$, 
with $s_{\rm min}=6 h^{-1} {\rm Mpc},\ s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalise these {\em clustering shells} as 
$\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}$
to nullify the amplitude information of the clustering signal, 
which is not associated with the Alcock-Paczynski test and is mostly sensitive to the galaxy bias.

The right panel of Fig.\ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
The contour lines are not horizontal due to the effects of peculiar velocity,
and the RSD effect clearly manifest itself through the tilting of contour lines.
However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimising the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects:
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong FoG effect near the LOS we take a cut $\mu_{\rm max} = 0.97$.

@@

The number of pairs are only counted in a fiducial cosmology
-- which is taken as the $\Omega_m=0.26$ $\Lambda$CDM --
and ``translated'' to the measurements in a ``target'' cosmology using the relations, 
\begin{eqnarray}
 s_{\rm target} = s_{\rm fiducial} \sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial}+\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}, \\
 \mu_{\rm target} = \mu_{\rm fiducial} \frac{\alpha_\parallel}
 {\sqrt{\alpha_{\parallel}^2 \mu_{\rm fiducial} +\alpha_{\bot}(1-\mu_{\rm fiducial}^2)}}
\end{eqnarray}
where $\alpha_{\bot}\equiv D_{A,\rm target}/D_{A,\rm fiducial}$,
$\alpha_{\parallel}\equiv H_{\rm fiducial}/H_{\rm target}$.
and values of $D_A$ and $H$ are computed in the effective redshifts of the six redshift bins.
In the fiducial cosmology
we measure $\xi(s,\mu)$ in an ultra high resolution of
$\Delta s = 0.2 {\rm Mpc/h}$, $\Delta \mu = 1/600$,
%Let us call this ``approximate 2pCF'' method.
%to obtain the accurate number counts 
and these small ``pixels'' are grouped to infer 
the number counts in other cosmologies, 
in large pixels of $\Delta s = 1 {\rm Mpc/h}$, $\Delta \mu = 1/120$.
%in the fiducial cosmology and group the bins in the target cosmology.
In the case when one small pixel belongs to more than one larger pixel (``edge effect'' ),
a correction is applied by computing the fraction of the overlapping area.
We found when using the approximate method the computed 
$\hat\xi_{\Delta s}(\mu)$ in a non-fiducial cosmology suffers from
an error of $\approx0.5\%$, which is 10 times smaller than 
the statistical noise in the 2pCF.

@@

The Planck team has released the {\texttt {COSMOMC}} \citep{LB2002} outputs of four MCMC ``chains'' in the CPL model, 
using a combination of four datasets:
the full-mission Planck observations of CMB temperature and polarization anisotropies \cite{Planck2015},
the BAO distance priors measured from SDSS DR11 \citep{Anderson2013}, 6dFGS \citep{6dFGS} and SDSS MGS \citep{MGS},
the ``JLA'' SNIa sample \citep{JLA},
and the Hubble Space Telescope measurement of $H_0=70.6\pm3.3$ \cite{Riess2011,E14H0}.
\footnote{http://pla.esac.esa.int/pla/\#cosmology}.
These MCMC chains contain the CMB+BAO+SNIa+$H_0$ likelihood computed for $\sim$37,000 sets of cosmological parameters,
yielding constraints of 
\begin{equation}
 \Omega_m = 0.309 \pm 0.010, w_0 = -0.938 \pm 0.109, w_a = -0.38 \pm 0.41.
\end{equation}
%To include the AP method into the constraints,
We then compute the likelihood of the LOWZ+CMASS AP measurements for each of the parameter combinations provided in the Planck chain. After multiplying the sample likelihoods with ours, while also changing the sample weights {\bf (HOW CHANGE?)}, we derive the CMB+BAO+SNIa+$H_0$+AP constraints on CPL parameters,
\begin{equation}
%\Omega_m = 0.300 \pm 0.008, w_0 = -1.056 \pm 0.061, w_a = -0.04 \pm 0.27,
    %1  0.2999656E+00  0.7616334E-02  0.2958745E+00  0.3035033E+00  0.2878169E+00  0.3132870E+00   \Omega_m
    %2  0.6904801E+00  0.8675444E-02  0.6808558E+00  0.6993898E+00  0.6722945E+00  0.7052207E+00   h
    %3 -0.1056468E+01  0.6096323E-01 -0.1116874E+01 -0.9965903E+00 -0.1175041E+01 -0.9287388E+00   w
    %4 -0.3808376E-01  0.2716607E+00 -0.3105235E+00  0.2321461E+00 -0.6033103E+00  0.4782076E+00   w_a    
\Omega_m = 0.301 \pm 0.008, w_0 = -1.042 \pm 0.067, w_a = -0.07 \pm 0.29.
%    1  0.3014353E+00  0.7759923E-02  0.2974325E+00  0.3048882E+00  0.2889838E+00  0.3152269E+00   \Omega_m
%    2  0.6887652E+00  0.8760036E-02  0.6797134E+00  0.6978279E+00  0.6703971E+00  0.7044224E+00   h
%    3 -0.1041626E+01  0.6732817E-01 -0.1107730E+01 -0.9768319E+00 -0.1172149E+01 -0.8979017E+00   w
%    4 -0.7173374E-01  0.2860547E+00 -0.3572176E+00  0.2107347E+00 -0.6775045E+00  0.4558817E+00   w_a    
\end{equation}
%$$.
While the central values of parameters do not shift appreciably,
the error bars of $w_0$ and $w_a$ are reduced by 38.4\% and 29.7\%, respectively.% $$-40\%$ by adding our method into the analysis.

The marginalised constraints on $w_0-w_a$ are shown in the left panel of Fig.\ref{fig_con}.
Adding our new AP constraints significantly reduces the allowable parameter space. 
This can also be visualise as allowable bands in $w(z)$ as can be seen in the right panel of Fig.\ref{fig_con}.

The derived cosmological constraints are fully consistent with a cosmological constant dark energy component having no evolution.
Adding the new AP method to the CMB+BAO+SNIa+$H_0$ constraints reduces the statistical errors by $\sim$30-40\%,
and reduces the 95.4\% CL $w_0-w_a$ contour by 50\%.
This reveals the constraining power of the small scale AP effect for probing the redshift evolution of dark energy.

@@

Finally, we performed a thorough test of all the possible variables in our methodology.
Figure \ref{fig_contest} shows that,
the result does not change if 
we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
decrease the number of angular bins to $n_{\mu}=15-20$,
change the range of clustering to $8-30 \rm Mpc/h$,
change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
exclude 1 or 2 high redshift bins,
or reduce the number of mocks to 1000.
%Constraints get weaker if increase $s_{\rm min}$,
%but are consistent with the original one.
%Even if we choose an extremely unrealistic fiducial cosmology, i.e. 
% $\Omega_m=0.11,\ w=-2.0$, the change in contour is still mild.
The most striking point to note in our testing is that the 
shift in contour position is very small even when we do not include the systematic correction.
This is reassuring, since we may have worried that {\it cosmological dependence} on the systematic correction could influence on our final results.

@@

In \cite{Li2016} we proposed to constrain cosmological parameters via 
the redshift dependence of galaxy anisotropic clustering. 
This enables a robust Alcock-Paczynski test on relatively small scales.
In this paper we improved the methodology and obtained tight constraints on the CPL parametrization of dark energy using 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12 spanning the redshift range $0.15<z<0.69$ . 
Adding our constraints to the CMB+SNIa+BAO+$H_0$ combination, the $w_0-w_a$ contour was reduced by $\sim50$\%.

The AP method presented in this work has many advantages over the `traditional' galaxy clustering method.
Since it works with the redshift evolution of the anisotropic clustering signal it significantly reduces the effect of systematics. 
It avoids the great difficulty in accurate modelling of the RSD, non-linear clustering and galaxy bias.
It is applicable on much smaller scales, allowing for the inclusion of more $k$-modes and hence more information.

@@

\begin{acknowledgments}
We thank the Korea Institute for Advanced Study for providing computing resources (KIAS Center for Advanced Computation Linux Cluster System).
CGS acknowledges support from the National Research Foundation (NRF,  \#2017R1D1A1B03034900). 
We thank Stephen Appleby, Seokcheon Lee, Maurice van Putten, Graziano Rossi and Yi Wang for helpful discussions.
\end{acknowledgments}
